### 2022-01-15 input/experiments.tex
results

@@

\begin{asparadesc}
\item [Objective:] Confirm the complexity analysis stating that
  communication and time overheads depend on the current partitioning
  of the system.

@@

\noindent Figure~\ref{fig:complexity} confirms that \NAME's overhead
depends on the size of partitions. The first partition is the most
expensive, for $\alpha$'s must reach every \process which takes time
and generate more traffic.  \NAME quickly converges towards consistent
partitioning in only 350 milliseconds. The last and $100^{th}$
partition added around 21 seconds is the least expensive. By using
scoped broadcast, control information only reaches a small subset of
the whole network.

@@

@@

\noindent Overall, this experimentation empirically demonstrates the
benefits of \NAME in the context of geo-distributed infrastructures,
e.g., inter-connected autonomous systems where \processes and
communications links may be added and removed at any time. \NAME
coupled with replication strategies designed for Edge infrastructures
would allow locking down the traffic of replica indexing, while
providing every \process with quick access to replicated content.

@@

\begin{figure*}
  \subfloat[PartA][\label{fig:europe-ases}An edge infrastructure
    comprising 40 interconnected autonomous systems spanning across
    Europe~\cite{knight2011internet}.]{
    \includegraphics[width=\FIGSCALE\columnwidth]{img/europe-ases.pdf}
  } \subfloat[PartB][\label{fig:xascast}
    \TODO{Experiment with ascast against xascast? with different cache
      size}]{
    \centering\includegraphics[width=\FIGSCALE\columnwidth]{img/europe_as_vs_xas.eps}
  }
  \caption{\TODO{Experiment measuring something on such a trace.} \TODO{Worst case when using as-cast}}
\end{figure*}

>>>>

%% \TODO{Each \process has a space complexity of $\mathcal{O}(\log_2(d \cdot
%% |V|))$, and generates messages of identical space complexity. In terms
%% of number messages, in the average case, a \process $x$ chosen
%% uniformly at random among all \processes creates a logical
%% partition. Its messages $\alpha_x$ spread through the network until
%% reaching \processes that belong to another partition closer to
%% them. This splits partitions in half on average. Overall, the $n^{th}$
%% new partition comprises \smash{$\mathcal{O}(\frac{|V|}{2^{\lfloor
%%       \log_2 n \rfloor}})$} \processes. This decreases every new
%% partition until reaching one \process per new partition: its
%% source. The average number of messages per \process is
%% \smash{$\mathcal{O}(\frac{\overline{|O|}}{2^{\lfloor \log_2 n
%%       \rfloor}})$}, where \smash{$\overline{|O|}$} is the average
%% number of neighbors per \process.}
%% \TODO{\TODO{Multiple receipt and multiple delivery} In terms of number of
%% messages, deleting the $a^{th}$ partition generates twice as many
%% messages as creating the $a^{th}$ partition: $\delta$ messages travel
%% through the partition, then $\alpha$ messages compete to fill the gap
%% \TODO{which is?}. \TODO{What about false positives?} Overall, the
%% communication complexity shows that \NAME scales well to the number of
%% partitions.}

%% In the
%% worst-case, every new partition includes all but one \process
%% belonging to the previous partition. The total number of messages
%% after the $a^{th}$ new partition is $\mathcal{O}(\overline{|O|}\cdot
%% a^2)$. As for the average-case, the number of messages for the
%% partition deletion is identical to the number of messages of the
%% corresponding partition creation.

@@

\begin{asparadesc}
\item [Objective:] Confirm the scalability of \NAME by higlighting the
  trade-off between the current partitioning of the system and the
  protocol's overhead in terms of traffic and termination time.

@@

\noindent Figure~\ref{fig:complexity} confirms that \NAME's overhead
depends on the size of partitions. In this scenario, it empirically
corresponds to a complexity in terms of number of messages of
$\mathcal{O}(\frac{|E|}{|V|\cdot|P|})$ where $E$ is the number of
links, $V$ is the number of \processes, and $P$ is the number of
partitions. In other terms, the $p^{th}$ partition contains $1/p$
\processes and reduces the size of closest partitions so every
partition has $1/p$ \processes on average.

\noindent Therefore, the first partition is the most expensive, for $\alpha$'s
must reach every \process which takes time and generate more traffic.
\NAME quickly converges towards consistent partitioning in only 350
milliseconds. The last and $100^{th}$ partition added around 21
seconds is the least expensive. By using scoped broadcast, control
information only reaches a small subset of the whole network.

@@

\begin{figure*}
  \subfloat {
    \includegraphics[width=\FIGSCALE\columnwidth]{img/europe-ases.pdf}
  }
  \hspace{5pt}
  \subfloat {
    \centering\includegraphics[width=\FIGSCALE\columnwidth]{img/europe_as_vs_xas.eps}
  }
  \caption{\label{fig:europe-ases}Traffic overhead and indexes
    maintained by \NAME and its extension \NAMEC in an Edge
    infrastructure comprising 40 interconnected autonomous systems of
    1157 \processes spanning across Europe~\cite{knight2011internet}}
\end{figure*}

@@

@@

\begin{asparadesc}
  \item[Objective:] Highlight the shortcoming of \NAME in Edge
    infrastructures and propose an improvement called \NAMEC (stands
    for \underline{cross} \underline{\NAME}) that fits this context by
    enabling lazy dynamic partitioning.

  \item[Description:] We build a network of networks by using an Edge
    infrastructure comprising 1157 \processes distributed in 40
    interconnected autonomous systems spanning across
    Europe~\cite{knight2011internet} as depicted in the left
    Figure~\ref{fig:europe-ases}. \emph{Gateway} \processes (dark in
    the figure) link autonomous systems together, \eg a Lisbon \node
    links Portugal to Spain and United Kingdoms through a Madrid \node
    and a London \node respectively.

    \noindent The left Figure~\ref{fig:europe-ases} depicts the
    operations executed during the simulation that lasts 7 seconds: at
    1 second, a \node located in Lisbon, Portugal performs an
    \texttt{Add}; at 2 seconds, a \node located in Palma de Majorque,
    Spain performs an \texttt{Add}; at 3 seconds, a \node located in
    Paris, France performs an \texttt{Add}; at 4 seconds, a \node
    located in Hvanneyri, Iceland performs an \texttt{Add}; and
    finally, at 5 seconds, the \node in Spain performs a \texttt{Del}.

    \noindent \NAMEC extends \NAME to enable lazy dynamic partitioning
    by allowing gateways to stop notifications when their respective
    network does not appear to have a source. Using \NAMEC, each
    \process maintains a \emph{local} index that corresponds to the
    best partition of its autonomous systems, and a \emph{global}
    index that corresponds to the best partition cross autonomous
    systems, \ie adjacent autonomous systems that have at least one
    source.

    \noindent We measure the number of messages transiting through the
    network for each operation, and we measure the number of
    \processes that index (\ie belong to a partition) over time.

  \item[Results:] Figure~\ref{fig:europe-ases} shows the results
    of this experiment. The top part highlights the cost of each
    partitioning protocol after each operation, while the bottom part
    provides the insight that explains these costs by displaying the
    number of indexes maintained by each protocol.

    \noindent Figure~\ref{fig:europe-ases} shows that Portugal's
    \texttt{Add} costs an order of magnitude more with \NAME compared
    to \NAMEC.  \NAME's messages propagate through all Europe, for
    \NAME regards Europe as 1 network of 1157 \processes while
    \NAMEC's messages propagate through Portugal's network of 23
    \processes only.

    \noindent Figure~\ref{fig:europe-ases} shows that Spain's
    \texttt{Add} costs slightly more with \NAMEC compared to \NAME.  A
    \process in Madrid links Portugal to Spain and the rest of
    Europe. Since Lisbon is closer to Madrid than Palma de Majorque
    is, only 11 \processes in Spain actually need to receive and
    deliver the new notification, hence the small overhead of this
    operation with \NAME. Using \NAMEC, the overhead is slightly
    higher since
    \begin{inparaenum}[(i)]
    \item the 20 \processes of Spain's network need to receive and
      deliver the new notification, \emph{and}
    \item Madrid's \process echoes Lisbon's notification as soon as it
      receives Palma's notification to 11 \processes.
    \end{inparaenum}

    \noindent Figure~\ref{fig:europe-ases} highlights the worst
    case scenario of \NAME: the cost of France's \texttt{Add} is close
    to that of Portugal's \texttt{Add} since it updates the whole
    Europe excluding Portugal and Spain. On the opposite, \NAMEC only
    updates France's 39 \processes.

    \noindent Figure~\ref{fig:europe-ases} shows that Iceland's
    \texttt{Add} has similar cost for \NAME and \NAMEC. Indeed, they
    both update Iceland, and when the notifications reach Copenhagen
    in Danemark, they stop either because France's notifications are
    closer (\NAME) or the Danish network does not have any source
    (\NAMEC).

    \noindent Finally, Figure~\ref{fig:europe-ases} shows that
    Spain's \texttt{Del} have similar cost for \NAME and
    \NAMEC. Nevertheless, the trade-off is different: \NAME's overhead
    comes from the 11 \nodes that need to acknowledge staleness and
    deliver the echos from Portugal; \NAMEC's overhead comes from the
    20 \nodes that need to acknowledge staleness. Using \NAMEC,
    Spain's network does not propagate echos since it does not have
    any source anymore.

%% \begin{asparadesc}
%%   \item[\TODO{Overall:}] this experimentation empirically demonstrates the
%%     benefits of \NAME in the context of geo-distributed
%%     infrastructures, e.g., inter-connected autonomous systems where
%%     \processes and communications links may be added and removed at
%%     any time. \NAME coupled with replication strategies designed for
%%     Edge infrastructures would allow locking down the traffic of
%%     replica indexing, while providing every \process with quick access
%%     to replicated content.
%% \end{asparadesc}

\TODO{Overall + transition.}
